Symmetry-based constraints on the size of the dynamical Solar neighborhood

### 2019-04-09 paper/ms.tex
Add bits about Solar circle

To illustrate this concept, we first compute the absolute range of midplane
values for a given $\Delta \phi$ segment of the midplane. With the observer's
azimuth set to zero, we consider a region extending from $-\Delta \phi/2$ to
$\Delta\phi/2$. To translate this angular scale into a physical scale, we also
compute the chord length $\lambda$ for the chord extending from the observer
to $\pm \Delta\phi/2$ (see Figure~\ref{fig:fig_to_explain}). We repeat this
for each of $50$ bins in azimuth. Each bin is plotted in
Figure~\ref{fig:range_deltaphi} as a gray line, with the mean value in solid
blue and the $1\,\sigma$ dispersion as the dashed blue lines.

\begin{figure*}
\plotone{fig/fig_to_explain.pdf}
\caption{A cartoon explanation of Figure~\ref{fig:range_deltaphi}. An observer
is placed at the blue x in the plane of a backgrround galaxy (lime). For a
given $\Delta \phi$ (blue) centered on the observer, we record the range of
midplane values for this section of the Solar circle (orange). We plot the
value of the range against the value of $\Delta \phi$. We are also able to
convert the value of $\Delta \phi$ into a chord length (pink), which we plot
as a secondary, upper $x$-axis. We repeat the procedure for each initial
$\phi$ (gray lines), and also compute the mean and $\pm1\,\sigma$ values (dark
blue).}
\label{fig:fig_to_explain}
\end{figure*}

\begin{figure*}
\plotone{fig/range_dphi.pdf}
\caption{The range of midplane heights encountered as a function of angular
width. At each angle $\phi$ from Figure~\ref{fig:midplane} we consider an
angular width of $\Delta \phi$ centered on $\phi$ and report the range of
midplane heights within that width. We repeat the procedure for each $\phi$
and plot the result as translucent gray lines. We also plot the mean range as
a solid blue line and the $\pm1\sigma$ lines as dashed blue lines. The upper
$x$-axis shows the chord length from the position $\phi$ to $\pm\Delta\phi/2$.
The horizontal \thincolor{} and \thickcolor{} lines shows the midplane
variation necessary to induce a $100\%$ error in $J_z$ for the thin-disk and
thick-disk orbits, respectively. A cartoon explanation of this Figure is given
in Figure~\ref{fig:fig_to_explain}.}
\label{fig:range_deltaphi}
\end{figure*}

>>>>

To illustrate this concept, we first compute the absolute range of midplane
values for a given $\Delta \phi$ segment of the midplane. With the observer's
azimuth set to zero, we consider a region extending from $-\Delta \phi/2$ to
$\Delta\phi/2$. To translate this angular scale into a physical scale, we also
compute the chord length $\lambda$ for the chord extending from the observer
to $\pm \Delta\phi/2$ (see Figure~\ref{fig:fig_to_explain}). We repeat this
for each of $50$ bins in azimuth. Each bin is plotted in
Figure~\ref{fig:range_deltaphi} as a gray line, with the mean value in solid
blue and the $1\,\sigma$ dispersion as the dashed blue lines. We choose to only consider the Solar circle to make the point that the midplane variation as a function of azimuth (and not just Galactic radius) is important. However, we note that because we use the range of midplane values, including regions of each galaxy outside the Solar circle can only act to increase this range, and therefore reduce the size of the dynamical solar neighborhood.

\begin{figure*}
\plotone{fig/fig_to_explain.pdf}
\caption{A cartoon explanation of Figure~\ref{fig:range_deltaphi}. An observer
is placed at the blue x in the plane of a backgrround galaxy (lime). For a
given $\Delta \phi$ (blue) centered on the observer, we record the range of
midplane values for this section of the Solar circle (orange). We plot the
value of the range against the value of $\Delta \phi$. We are also able to
convert the value of $\Delta \phi$ into a chord length (pink), which we plot
as a secondary, upper $x$-axis. We repeat the procedure for each initial
$\phi$ (gray lines), and also compute the mean and $\pm1\,\sigma$ values (dark
blue). We only consider the Solar circle to explore the impact of azimuthal midplane variations, but similar effects are expected for radial midplane variations.}
\label{fig:fig_to_explain}
\end{figure*}

\begin{figure*}
\plotone{fig/range_dphi.pdf}
\caption{The range of midplane heights encountered as a function of angular
width. At each angle $\phi$ from Figure~\ref{fig:midplane} we consider an
angular width of $\Delta \phi$ centered on $\phi$ and report the range of
midplane heights within that width. We repeat the procedure for each $\phi$
and plot the result as translucent gray lines. We also plot the mean range as
a solid blue line and the $\pm1\sigma$ lines as dashed blue lines. The upper
$x$-axis shows the chord length from the position $\phi$ to $\pm\Delta\phi/2$.
The horizontal \thincolor{} and \thickcolor{} lines shows the midplane
variation necessary to induce a $100\%$ error in $J_z$ for the thin-disk and
thick-disk orbits, respectively. A cartoon explanation of this Figure is given
in Figure~\ref{fig:fig_to_explain}. We only consider the Solar circle to explore the impact of azimuthal midplane variations, but similar effects are expected for radial midplane variations.}
\label{fig:range_deltaphi}
\end{figure*}
